Phonetic Transcription by Untrained Annotators

### 2018-06-04 2018-itat-krompachy/paper.tex
more itat 2018 text

We can also track how the scenario described in
subsection~\ref{subsec:respelling} is applied. We have looked up four promising
example records in the dynamic dictionary and checked submitted transcriptions
containing them. Table~\ref{tab:pronunc}

\begin{table}[htpb]
\begin{center}
\begin{tabular}{|l r|l r|l r|l r|}
\hline
Correct written form        & \#
	& wrong phonetic pronunc.   & \#
		& correct pronunc.          & \#
			& phon. respelling          & \# \\
\hline
Moody & 2 & {\texttt m o o d i} & 0 & {\texttt m uu d i} & 4 & {\em múdy}, {\em můdy} & 2 \\
Descartes & 2 & {\texttt d e s c a r t e s} & 0 & {\texttt d e k aa r t} & 4 & {\em dekárt} & 2   \\
Weinfurter & 18 & {\texttt v e j n f u r t e r} & 9 & {\texttt v a j n f u r t r} & 16 & {\em vajnfurtr} & 9 \\
Michelangelo & 6 & {\texttt m i x e l a ng g e l o} & 9 & {\texttt m i k e l a n dzh e l o} & 9 & {\em mikelan'dželo} & 4 \\
\hline
\end{tabular}
\caption{Examples of non-standard pronunciation in the manually transcribed data}\label{tab:pronunc}
\end{center}
\end{table}

>>>>

We can also track how the scenario described in
subsection~\ref{subsec:respelling} is applied. We have looked up four promising
example records in the dynamic dictionary and checked submitted transcriptions
containing them. Table~\ref{tab:pronunc} lists for each of them the correct
orthographic form, the wrong pronunciation obtained by the transducer, the
correct pronunciation and finally the phonetic respelling. Each is followed by
the number of occurrences in the manually transcribed data.

\begin{table}[htpb]
\begin{center}
\begin{tabular}{|l r|l r|l r|l r|}
\hline
Correct written form        & \#
	& wrong phonetic pronunc.   & \#
		& correct pronunc.          & \#
			& phon. respelling          & \# \\
\hline
Moody & 2 & {\texttt m o o d i} & 0 & {\texttt m uu d i} & 4 & {\em múdy}, {\em můdy} & 2 \\
Descartes & 2 & {\texttt d e s c a r t e s} & 0 & {\texttt d e k aa r t} & 4 & {\em dekárt} & 2   \\
Weinfurter & 30 & {\texttt v e j n f u r t e r} & 13 & {\texttt v a j n f u r t r} & 19 & {\em vajnfurtr} & 2 \\
Michelangelo & 6 & {\texttt m i x e l a ng g e l o} & 2 & {\texttt m i k e l a n dzh e l o} & 4 & {\em mikelandželo} & 0 \\
\hline
\end{tabular}
\caption{Examples of non-standard pronunciation in the manually transcribed data}\label{tab:pronunc}
\end{center}
\end{table}

\begin{table}[htpb]
\begin{center}
\begin{tabular}{|l|r|r|}
\hline
 & phonetically correct & phonetically incorrect \\
orthographically correct & 25 & 15 \\
orthographically incorrect & 6 & 0
\hline
\end{tabular}
\caption{Success rate for phonetic and orthographic representation of foreign
words}\label{tab:pronunc-rate}
\end{center}
\end{table}

We can see in Table~\ref{tab:pronunc-rate} that the majority of cases results in
both orthographic and phonetic forms being correct. Only in about 13\% cases,
the orthographically incorrect form is kept. We attribute this to the fact that
those who use the phonetic transcription are aware of the problematic and mostly
go the whole way and clean up.

On the other hand, nearly a third of the cases show the wrong phonetic
representation. This is a serious problem on at least two levels: Firstly, it
shows that the forced aligner failed to catch the error. Secondly
